The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-28 paper/sections/results.tex
edits

In \reffig{teaser} we directly simulate the NURBS surface model of a bouncy castle under a periodic wind force. 
In \reffig{starship} we show an animation of the Space-V starship landing on Mars in a graceful way. Our SEM successfully handles the stiff materials, complicated geometry and non-trivial collisions in the scene.

>>>>

In \reffig{teaser} we directly simulate the NURBS surface model of a bouncy castle under a periodic wind force. 
In \reffig{starship} we show an animation of the Space-V starship landing on Mars in a graceful way. 
This example shows the benefit of NURBS modeling, a relatively small number of primitives can represent a complex shape.
SEM successfully handles the stiff materials, complicated geometry and non-trivial collisions in this scene.
